---
title: "R Notebook"
output: 
  html_notebook: 
    fig_caption: yes
---


Read the data and format dates

```{r}
library(tidyverse); library(readr); library(lattice)
source("exploratoria_vento_prepare_dataset.R")

```

# Exploratory Analysis

## Does the year profile is kept across months for the different locations?

```{r}
result <- WindData_melt %>% group_by(MONTH1, location) %>% summarise(mean = mean(wind)) 
xyplot(mean~MONTH1, data= result, type = "l", groups = location, auto.key = TRUE)
```

```{r}
result <- WindData_melt %>% group_by(MONTH1, location,YEAR1) %>% summarise(mean = mean(wind)) 
xyplot(mean~MONTH1 | YEAR1, data= result, type = "l", groups = location, auto.key = TRUE)
```


## Have month in different years the same distribution?

At first, we look how each year differ from each other.



```{r fig.cap="Teste densidade"}
densityplot(~W1 | factor(MONTH1), group = YEAR1,data = WindData, main="Density comparison across different years", auto.key = TRUE, xlab = "")
densityplot(~W1 | factor(MONTH1), group = YEAR1,data = WindData_melt, main="Density comparison across different years", auto.key = TRUE)
densityplot(~W1 | factor(MONTH1),data = WindData, main="Wind power density comparison across different months", xlab = "")

plot(WindData$W1, lag(WindData$W1))
```
As we can see in the graph,  



```{r}
densityplot(~W2 | factor(MONTH1), group = YEAR1,data = WindData, main="Density comparison across different years", auto.key = TRUE)
```



asdfsd

```{r}
densityplot(~W3 | factor(MONTH1), group = YEAR1,data = WindData, main="Density comparison across different years", auto.key = TRUE)
```

asdfd

```{r}
densityplot(~W4 | factor(MONTH1), group = YEAR1,data = WindData, main="Density comparison across different years", auto.key = TRUE)
```



## How does hour of the day influence the distribution

Looking for the distribution of each hour as a whole, we notice pontual differences in distribution across years for each hour. This fact is consistent among different series 

```{r}
  densityplot(~W6 | factor(HOUR1), group = YEAR1,data = WindData, main="Density      comparison across different hours and years", auto.key = TRUE)
```

```{r}
  densityplot(~W1 | factor(HOUR1), group = YEAR1,data = WindData, main="Density      comparison across different hours and years", auto.key = TRUE)
```



But what about the hour profile across different months. How does it behave?

```{r fig.height=16, fig.width=8}

  densityplot(~W1 | factor(HOUR1), group = MONTH1,data = WindData, main="Density      comparison across different hours and years", auto.key = TRUE)
```



```{r fig.height=16, fig.width=8}
  densityplot(~W1 | factor(MONTH1), group = HOUR1,data = WindData, main="Density      comparison across different hours and years", auto.key = FALSE)
```

